landlord

### 2022-10-26 src/landlord.Rmd
pick up on line 61
double checked scoring. Corrected security deposit limit

#security_deposit_limit
MSA_landlord_data <- MSA_landlord_data %>% 
  mutate(
    security_depopsit_limit_num = case_when(
      security_deposit_limit == "N" ~ 1.0, 
      security_deposit_limit == "1_month_rent" ~ 0.5,
      security_deposit_limit == "2_months_rent" ~ 0.0))

@@

```{r}
#calculate landlord category score

>>>>

#security_deposit_limit
MSA_landlord_data <- MSA_landlord_data %>% 
  mutate(
    security_depopsit_limit_num = case_when(
      security_deposit_limit == "N" ~ 1.0, 
      security_deposit_limit == "1_month_rent" ~ 0.0,
      security_deposit_limit == "2_months_rent" ~ 0.5))

@@

```{r}
#PICK UP HERE!
#calculate landlord category score
